Analytic Occultation Light Curves in Reflected Light

### 2020-05-04 tex/ms.tex
more figs

\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/earthmoon_emitted.pdf}
        \includegraphics[width=\linewidth]{figures/earthmoon.pdf}
        \oscaption{earthmoon}{%
            Mock light curves of the Moon occulting a rotating,
            cloudless Earth expanded to spherical harmonic degree $l = 25$.
            Black curves show the analytic solution; orange dots correspond
            to brute force numerical integration on a grid of
            ${\sim}10^6$ points.
            The top panel shows the light curve in emitted light and is
            equivalent to Figure~7 in \citet{Luger2019}.
            The bottom panel (this work) shows the same light curve in
            reflected light during northern summer.
            \label{fig:earthmoon}
        }
    \end{centering}
\end{figure}

@@

\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/speed.pdf}
        \oscaption{speed}{%
            Evaluation time (vertical axis)
            and numerical precision (point size)
            for a single flux evaluation as a function of spherical
            harmonic degree for different methods.
            In orange we show results for the emitted light
            \starry algorithm from \citet{Luger2019} (solid: no gradient,
            dashed: with gradient), and in blue we show results for
            the reflected
            light algorithm from this paper (solid: no gradient,
            dashed: with gradient). For comparison, in purple we show
            results for discrete integration on a grid (solid) and
            numerical integration using two-dimensional Gaussian
            quadrature (dashed); neither of these include gradient
            evaluations. The reflected light algorithm is around one
            order of magnitude slower and less precise than the emitted
            light algorithm, but still ${\sim}4$ orders of magnitude faster
            and ${\sim}10$ orders of magnitude more precise than numerical
            integration.
            \label{fig:speed}
        }
    \end{centering}
\end{figure}

@@

\subsection{Extended illumination source}
\label{sec:extended}
Planets to consider: 55 Cnc e, Kelt-9b.
The angular extent of the terminator past $\nicefrac{\pi}{2}$ is
%
\begin{align}
    \tau = \arcsin\left( \frac{\Delta R}{d} \right)
\end{align}

@@

\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/oren_nayar.pdf}
        \oscaption{oren_nayar}{%
            Phase curves for different surface roughness coefficients.
            \label{fig:oren_nayar}
        }
    \end{centering}
\end{figure}
%

@@

\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/io_europa.pdf}
        \oscaption{io_europa}{%
            Occultation of Io by Europa.
            \label{fig:io_europa}
        }
    \end{centering}
\end{figure}
%

>>>>

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/earthmoon_emitted.pdf}
        \includegraphics[width=\linewidth]{figures/earthmoon.pdf}
        \oscaption{earthmoon}{%
            Mock light curves of the Moon occulting a rotating,
            cloudless Earth expanded to spherical harmonic degree $l = 25$.
            Black curves show the analytic solution; orange dots correspond
            to brute force numerical integration on a grid of
            ${\sim}10^6$ points.
            The top panel shows the light curve in emitted light and is
            equivalent to Figure~7 in \citet{Luger2019}.
            The bottom panel (this work) shows the same light curve in
            reflected light during northern summer.
            \label{fig:earthmoon}
        }
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/speed.pdf}
        \oscaption{speed}{%
            Evaluation time (vertical axis)
            and numerical precision (point size)
            for a single flux evaluation as a function of spherical
            harmonic degree for different methods.
            In orange we show results for the emitted light
            \starry algorithm from \citet{Luger2019} (solid: no gradient,
            dashed: with gradient), and in blue we show results for
            the reflected
            light algorithm from this paper (solid: no gradient,
            dashed: with gradient). For comparison, in purple we show
            results for discrete integration on a grid (solid) and
            numerical integration using two-dimensional Gaussian
            quadrature (dashed); neither of these include gradient
            evaluations. The reflected light algorithm is around one
            order of magnitude slower and less precise than the emitted
            light algorithm, but still ${\sim}4$ orders of magnitude faster
            and ${\sim}10$ orders of magnitude more precise than numerical
            integration.
            \label{fig:speed}
        }
    \end{centering}
\end{figure}

@@

\subsection{Extended illumination source}
\label{sec:extended}
Planets to consider: 55 Cnc e, Kelt-9b.
Assuming $R_\star > R_p$, the angular extent of the terminator
past $\nicefrac{\pi}{2}$ is
%
\begin{proof}{}
    \label{eq:tau}
    \tau &= \arcsin\left( \frac{R_\star - R_p}{d} \right)
\end{proof}
%
where $R_\star$ is the radius of the star,
$R_p$ is the radius of the planet, and $d$ is the separation of their
centers.

For Kelt-9b, $\nicefrac{R_p}{R_\star} = 0.083$ and
$\nicefrac{a}{R_\star} = 3.16$, where $a$ is the semi-major axis of the
planet \citep{Wong2019}. Asssuming zero eccentricity and ignoring any
stellar oblateness
\citep[see][]{Ahlers2020}, we find that
the day/night terminator extends $\tau \approx 17^\circ$ past the limb
of the planet. Figure~\ref{fig:extended} shows...

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/extended.pdf}
        \oscaption{extended}{%
            Normalized surface intensity on Kelt-9b viewed in a
            Mollweide projection assuming a point illumination source
            (left) and accounting for the finite extent of the star
            (right). The day/night terminator extends about $17^\circ$
            past where it is in the point source case. The sub-stellar
            intensity is higher in the extended source case because the
            sub-planet point on the star is 
            closer to the planet than in the case where the star is a point
            source located at the center of the star.
            \label{fig:extended}
        }
    \end{centering}
\end{figure}

Figure~\ref{fig:kelt9b} shows...

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/kelt9b.pdf}
        \oscaption{kelt9b}{%
            Reflected light phase curve model (left) and
            secondary eclipse model for Kelt-9b, assuming
            a spherical albedo $A = 0.2$. The transit (phase zero)
            is not included. Blue is the \starry model
            assuming a point source illumination; orange accounts for
            the finite size of the star. The right panel shows
            the normalized flux during secondary eclipse ingress
            for the two \starry models and for two approximations:
            a surface with uniform intensity (solid purple)
            and a surface whose intensity falls as the cosine of the
            viewing angle from the center of the planet disk
            (dashed purple).
            \label{fig:kelt9b}
        }
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/oren_nayar.pdf}
        \oscaption{oren_nayar}{%
            Intensity measured from a sphere at varying illumination
            phase under the \citet{OrenNayar1994} scattering model.
            The top panel shows spheres rendered with different surface
            roughness coefficients ranging from $\sigma = 0^\circ$
            (the Lambertian case) to $\sigma = 45^\circ$. The bottom
            panel shows the corresponding phase curves for a sphere
            of unit spherical albedo illuminated by a point source
            at $r_s = 1$, computed
            analytically from a degree \STARRYQUADPOINTS expansion
            of the scattering law. Dots
            correspond to the intensity computed numerically directly
            from Equation~(30) in \citet{OrenNayar1994}.
            \label{fig:oren_nayar}
        }
    \end{centering}
\end{figure}
%

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/io_europa.pdf}
        \oscaption{io_europa}{%
            Visible-light occultation of Io by Europa observed
            on 04 Dec 2009 by the PHEMU09 campaign \citep{Arlot2014}.
            The blue line is the \starry model, based of an
            $l=15$ spherical harmonic fit to the
            Galileio global color mosaic of Io \citep{Becker2005},
            an $l=\STARRYQUADPOINTS$ expansion of the
            \citep{OrenNayar1994} scattering law, and orbital
            information from the JPL Horizons \xxx{(cite)} database.
            See text for details.
            \label{fig:io_europa}
        }
    \end{centering}
\end{figure}
%
